---
title: "Simple document"
output: 
  github_document
---

```{r}
library(tidyverse)
```

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(1000)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

If roundup the mean: round(mean(samp),#round up num)
ex: round up 2: round(mean(samp),2)

# Section 3

This is going to make a plot! First I gengerate a dataframe, then use " ggplot" to make a scatterplot.
control, alt, I-->
echo= FALSE
message = FALSE
```{r chunk_scatterplot, echo=FALSE}
plot_df =
  tibble(
    x= rnorm(n=1000),
    y= 1 + 2 * x + rnorm(n=1000)
  )
ggplot(plot_df, aes(x=x, y=y)) + geom_point()

```
```{r chunk_histogram}
ggplot(plot_df, aes(x=x, y =y)) + geom_point()
```

Quick solution on the website
```{r}
la_df=
   tibble(
    norm= rnorm(n=500, mean = 1),
    logical = norm > 0,
    abs_norm = abs(norm),
    round(median(norm),2)
  )

ggplot(la_df, aes(x= abs_norm)) + geom_histogram()
```
Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

